---
title: "Week 2"
author: "Thang"
date: "6/23/2021"
output: html_document
---

```{r echo=FALSE, message=FALSE}
library(tidyverse)
library(statsr)
```
<div class="question">
Question 1.
Answer: The posterior is a mixture of prior and the likelihood - as we 
collect data we expect the likelihood will be favored over the prior. In
this case with 10 observed data points we would expect the posterior to
shift further from the prior.
</div>

<div class="question">
Question 4. Question 4
If you are told that the prior for parameter \thetaθ has a distribution from family A and that it is conjugate to the likelihood from family B, then to which distribution family will the posterior belong?

* The posterior will belong to the B family
* We need to know more about the 2 distributions
* The posterior will belong to the A family
</div>

Answer: If a prior is conjugate to the likelihood, the posterior will have the same distribution as the prior

<div class="question">
Question 5. You are hired as a data analyst by politician A. She wants to know the proportion
of people in Metrocity who favor her over politician B. From previous poll
numbers, you place a Beta(40,60) prior on the proportion. From polling 200
randomly sampled people in Metrocity, you find that 103 people prefer politician
A to politician B. What is the posterior probability that the majority of
people prefer politician A to politican B (i.e. P(p>0.5|data))? 

* 0.198
* -> 0.209
* 0.664
* 0.934
</div>

```{r}
1-pbeta(q = 0.5, shape1 = 40+103, shape2 = 60 + 200 - 103)
```

<div class="question">
Question 6. A young meteorologist is trying to estimate the expected number of tropical cyclones that occur in a given year.  He assumes that the number of observed tropical cyclones in a year follows a Poisson distribution with rate $\lambda$ that is consistent across years.  Because the meteorologist is inexperienced, he assigns a relatively uninformative Gamma(k = .5,\theta = 2)Gamma(k=.5,θ=2) prior distribution to $\lambda$.  During his first five years, he observes a total of 49 cyclones.  If he were to collect more data about tropical cyclones in future years, what should his prior be?? 

* Gamma (k=49.5, theta = 7)
* Gamma (k=49.5, theta = 2/21)
* -> Gamma (k=49.5, theta = 2/11)
* Gamma (k=49, theta = 7)
</div>

<div class="question">
Question 10. Suppose you are given a die and told that the die is either fair or is loaded (it
always comes up as a 6). Since most dice are not loaded, you place a prior
probability of 0.8  on the outcome that the die is fair. You roll a die and it comes up as a 6. 
What is the posterior probability that your next roll will also be a 6?

*4/5
*3/5
*11/15
*-> 2/3
</div>

After the first dice, the posterior of the dice is fair is 

```{r}
post <- 1/6*0.8/(1/6*0.8+1*0.2)
```

Because, a dice has 6 value. The probability of the dice coming up as 6 is 1/6. 
The total probability of the dice is 1, because we think it is fair.

If the next roll will also be 6, then the probability is the sum of

(the probability when it fair and got 6 + the probability when it is loaded)

```{r}
1/6*post+(1-post)*1
```

<div class="question">
True or False: When constructing a 95% credible interval, a good rule of thumb is to use the shortest of all such intervals

* -> True
* False
</div>

